Multi-Agent Reinforcement Learning in Zombie-Survival Games

### 2020-12-16 paper/paper.tex
update paper

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsfonts}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

In (\ref{sec:background}) we review Markov Decision Processes (MDPs), the Actor-Critic algorithm, MADDPG, and agent design.
In (\ref{sec:game}) we detail the basic simulation environment.
In (\ref{sec:baseline}) we detail the experimental setup and initial results.
In (\ref{sec:anon}) we investigate partial observability, and how compression of the observation function can speed policy discovery.
In (\ref{sec:health}) we alter the environment to cause a change in the value function (keeping reward unchanged) to study the impact on learned policies.
In (\ref{sec:arms}) we arm the survivors with projectile weapons to investigate how additional capability can make it harder for agents to achieve their objectives.

@@

\subsection{Actor-Critic methods}

@@

In Actor-Critic (AC), both a policy (the actor) and an action-value function (the critic) are learned.
The Critic is used to estimate the policy gradient (the direction of changes to the policy parameters that cause actions that generate higher expected returns),
which is then used to update the policy function parameters at each training step.

@@

The Markov Decision Process (MDP) framework regards other agents as part of the environment from the perspective of a single agent;
so if other agents in the environment are learning and modifying their behaviour then the environment contains shifting dynamics (the environmental data-generating process is considered non-stationary).
Deep Deterministic Policy Gradient (DDPG) is an actor-critic algorithm used in continuous control tasks.
It was shown in () that the chance of sampling a policy-gradient update in an improved direction decreases exponentially with the number of agents being trained in the shared environemnt.

MADDPG is a modified actor-critic method designed to address the stabilitiy issues due to the simultaneous learning of policies in the multi-agent setting.
A key component of MADDPG is the use of a shared critic that has access to the policies of all other agents during training.
In MADDPG, agents can have different state and action spaces, and be goverened by different reward functions.
We use the MADDPG algorithm for all agents within our scenarios.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amsmath}
\renewcommand{\UrlFont}{\ttfamily\small}

@@

In (\ref{sec:background}) we review theory, RL algorithms, and aspects of agent design.
In (\ref{sec:game}) we detail the basic simulation environment.
In (\ref{sec:baseline}) we detail the experimental setup and initial results.
In (\ref{sec:anon}) we investigate partial observability, and how compression of the observation function can speed policy discovery.
In (\ref{sec:health}) we alter the environment to cause a change in the value function (keeping reward unchanged) to study the impact on learned policies.
In (\ref{sec:arms}) we arm the survivors with projectile weapons to investigate how additional capability can make it harder for agents to achieve their objectives.

@@

\subsection{DDPG}

@@

Policy-gradient (PG) methods learn a policy $\pi_\theta$, parameterized by $\theta$,
by sampling the gradient of a performance measure $J(\theta)$ with respect to $\theta$.

\begin{equation}
  \nabla_\theta J(\theta)=\mathbb{E}_\pi\left[Q^\pi(s, a) \frac{\nabla_\theta\pi_\theta(a|s)}{\pi_\theta(a|s)}\right]
\end{equation}

REINFORCE, a simple PG algorithm, uses all the steps in an episode to find $Q^\pi(s,a)=\mathbb{E}_\pi[G|s,a]$, where $G$ is the total reward of an episode.
Because reward functions sometimes give high values for some states, this method can give high variance gradient estimates.
This can be remedied by using a baseline $b(s)$:

\begin{equation}
  \nabla_\theta J(\theta)=\mathbb{E}_\pi\left[(G-b(s)) \frac{\nabla_\theta\pi_\theta(a|s)}{\pi_\theta(a|s)}\right]
\end{equation}

Actor-Critic (AC) improves on REINFORCE by learning a state-value function with baseline (critic), and an action-value function (actor) concurrently.
AC also has the advantage that the parameters for both functions are updated at every step in an episode.
The policy gradient at each time step $t$ can be expressed:

\begin{equation}
  \nabla_\theta J(\theta)=\mathbb{E}_\pi\left[\delta_t \frac{\nabla_\theta\pi_\theta(a|s)}{\pi_\theta(a|s)}\right]
\end{equation}
\begin{equation}
  \delta_t = r_{t+1}+\gamma \hat{v}(s_{t+1}, w)-\hat{v}(s_t,w)
\end{equation}

where $\gamma$ is a discount parameter, and $\hat{v}(w)$ the state-value function with parameters $w$.

Deterministic Policy Gradient (DPG) methods extend policy gradient to deterministic policies.
A deterministic policy ($\mu_\theta$) maps a state to an action,
whereas a stochastic policy ($\pi_\theta$) provides a conditional probability of an action in a given state.

\begin{equation}
  \nabla_\theta J(\theta)=\mathbb{E}_s\left[\nabla_\theta \mu_\theta(a|s) \nabla_a Q^\mu(s,a)|_{a=\mu_\theta(s)}\right]
\end{equation}

DPG methods are often used in continuous control tasks
(taking the gradient of $Q^\mu$ with respect to $a$ requires the action space to be continuous).

Deep Deterministic Policy Gradient (DDPG) combines ideas from DPG and DQN.
In DDPG the actor and critic are approximated with neural networks.
DDPG uses target networks for both actor and critic, and makes use of an experience replay buffer to store agent trajectories.

@@

The Markov Decision Process (MDP) framework regards other agents as part of the environment from the perspective of a single agent.
From the perspective of an agent, the influence on rewards from other agents in the environment can make it harder to learn a policy;
this is especially so when the environment contains other agents that are also learning policies,
because elements of the `environment' change while the agent is trying to learn them.

It was shown in () that the chance of sampling a policy-gradient update in an improved direction decreases exponentially with the number of agents being trained in the shared environemnt.

MADDPG addresses this stabilitiy issue by using centralized critics.
In MADDPG, the critic $Q^\pi_i(x, a_1, a_2, ..., a_N)$ for agent $i$ has access to the actions of all $N$ agents, and some state information $x$.
The critic is often only used in training, so it's possible to deploy MADDPG actors in continuous control tasks where knowledge of other actors' actions are not available.
Agents can have different state and action spaces, and be goverened by different reward functions.
We use the MADDPG algorithm for all agents within our scenarios.
